\thetitle

### 2024-11-05 paper/paper.tex
Add notes for Next steps

TODO: Discuss \citet{riess1998}, \citet{perlmutter1999}, and \citet{perlmutter2003}, as well as their nobel prize, summarizd in \citet{straumann2012}.

@@

Luminosity distance, $D_L$, is the appearant distance of an object based on the
measured luminosity. This does not take into account any movement of the
observed object between the time when the light was emitted and the light is
observed.

@@

We note that since all Type Ia supernova have approximately the same intrinsic
brightness, we can use a geometric model to compute relative distances. Imagine
holding up two coins, one in each hand.  If you arange them so that the
distance from your eyes to the first coin double the distance from your eyes to
the second coin, the second coin should appear to be $\frac{1}{4}$ of the size.
More formally, for two objects of the same radius $r$, the appearant area $A$
is

@@

>>>>

TODO: Discuss \citet{riess1998}, \citet{perlmutter1999}, and \citet{perlmutter2003}, as well as their nobel prize, summarized in \citet{straumann2012}.

@@

Luminosity distance, $D_L$, is the apparent distance of an object based on the
measured luminosity. This does not take into account any movement of the
observed object between the time when the light was emitted and the light is
observed.

@@

We note that since all Type Ia supernova have approximately the same intrinsic
brightness, we can use a geometric model to compute relative distances. Imagine
holding up two coins, one in each hand.  If you arange them so that the
distance from your eyes to the first coin double the distance from your eyes to
the second coin, the second coin should appear to be $\frac{1}{4}$ of the size.
More formally, for two objects of the same radius $r$, the apparent area $A$
is

@@

If that's accurate, it would be interesting to repeat the computation of
cosmological constants. Is there evidence for acceleration or deceleration
for the expansion rate?

Find a bigger dataset. Use \citet{abbott2024} perhaps?

Is it necessary to figure out a hypothesis test? What would that even look
like?
